Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-12-29 WSSSPE2_report/WSSSPE2_review.tex
Remove unmatched right parenthesis

\begin{figure}[!ht]
  \centering
    \includegraphics[width=1.0\textwidth]{figures/barriers}
  \caption{Barriers to software sustainability, showing the fraction of attendees (rounded to the nearest 10\%) who voted for an item as important.
{\footnotesize \newline (1) This item also included the fact that that the promotion and tenure process in academic is incompatible with sustainability.
\newline  (2) The software engineering practices were those in particular that are needed to scale-up projects to support and be developed by a large sustainable community).
\newline  (3) The smallest number of key people a project would need to lose to become
non-viable -- the larger the number, the healthier the project.}
\label{fig:software_sustainability_barriers}}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
    \includegraphics[width=1.0\textwidth]{figures/barriers}
  \caption{Barriers to software sustainability, showing the fraction of attendees (rounded to the nearest 10\%) who voted for an item as important.
{\footnotesize \newline (1) This item also included the fact that that the promotion and tenure process in academic is incompatible with sustainability.
\newline  (2) The software engineering practices were those in particular that are needed to scale-up projects to support and be developed by a large sustainable community.
\newline  (3) The smallest number of key people a project would need to lose to become
non-viable -- the larger the number, the healthier the project.}
\label{fig:software_sustainability_barriers}}
\end{figure}
